Universal Anonymous Signatures

### 2022-08-08 prism-backend/research/gsac/app-uas-proofs.tex
Updated proofs for sign-unforgeability, and non-frameability.

  If the verification at line 4 of \ExpForgeSign holds, then $(\msg,\feval,
  \yeval,\cinsp,\sipk,\opk,\widetilde{\Eek}) \in \NIZKLang^{\Sign}$. Then:
  %

  \paragraph{(a) \Judge accepts $(\yinsp,\iproof)$.} %
  Simulation extractability of $\NIZK^{\Sign}$ thus ensures that $\cinsp =
  \EEnc(\Eek,\yinsp)$, and since $(\yinsp,\iproof)$ is generated honestly at
  line 5, then \yinsp is the correct decryption of \cinsp, and  correctness of
  $\NIZK^{\Open}$ ensures that \Judge outputs $1$ at line 6.

@@

  \paragraph{(c) The output of \finsp matches the output of \Open.} %
  After (a), the \yinsp value output by \Open is the correct decryption of
  \cinsp. After (b), the $(\yeval^0=\yeval,\yeval^1)$ values output by
  \ExtractSign match the evaluation of \feval. Thus, simulation extractability
  of $\NIZK^{\Sign}$ ensures that $\finsp((\yeval^0,\yeval^1),\upk,\lbrace
  (\cid_i,\attrs_i)\rbrace_{i\in[n]},\msg) = \yinsp$ and, also, that \yinsp
  matches the $\yinsp'$ value extracted by \ExtractSign. Thus, the probability
  of \adv~winning at line 10 is negligible due to simulation extractability
  of $\NIZK^{\Sign}$.

  \paragraph{(d) All {\cred}s are bound to the same \usk.} %
  $\NIZKRel^{\Sign}$ includes a condition that $\forall i\in[n],
  \SBCMVerify(\ipk_i,\cred_i,\usk,\attrs_i) = 1$. Thus, simulation
  extractability of $\NIZK^{\Sign}$ and correctness of \SBCM, ensure that all
  credentials involved in the signature contain \usk as their user key (first)
  attribute. Consequently, \IdentifyCred returns $1$ for all the involved
  credentials, and the probability of \adv~winning at line 11 is $0$.

  \paragraph{(e) \usk must belong to a known user.} %
  The only remaining option for $\adv$ to win is via winning condition at line
  12, meaning that \IdentifySig fails to find an honest or corrupt users with
  a \usk matching the one used to request the credentials used to produce the
  signature output by \adv. However, at line 12, we already know that all
  credentials are valid signatures by the issuer and that, also, all are bound
  to the same user key. If this key is not associated to any known user, this
  means that there is no matching $\langle\Obtain,\Issue\rangle$ transcript for
  a credential over \usk --i.e., the honest issuer did not issue any credential
  to \usk. But, as \sig must have been produced with at least one credential
  (extracted at step 7), then this credential is a forgery, breaking security
  against one-more forgery of the \SBCM scheme.
  %
  \qed
\end{proof}

@@

  First, suppose that the \Sig that \adv~outputs at line 2 exists in
  \SIG, for some \uid. Then, Given that the signature is accepted by \Verify at
  line 3, and after simulation extractability of $\NIZK^{\Sign}$, $\yeval =
  \yeval^0$, and $\tyeval^1 = \yeval^1$. Similarly, since the $(\yinsp,\iproof)$
  pair output by \adv~is accepted by \Judge, simulation extractability of
  $\NIZK^{\Sign}$ and $\NIZK^{\Open}$ implies that both checks at lines 7 and 8
  pass. Hence, the probability that the adversary wins at either lines 7 or 8 is
  negligible, after simulation extractability of $\NIZK^{\Sign}$ and
  $\NIZK^{\Open}$.

@@

  Consider game $G_1$, which is equivalent to $G_0 = \ExpNonframe$, except that
  in the \Sign function within the \SIGN oracle, we simulate the NIZK proof.
  After the zero-knowledge property of $\NIZK^{\NIZKRel_{\Sign}}$, $G_1$ is
  indistinguishable from $G_0$. Now, in $G_1$, simulation extractability of
  $\NIZK^{\NIZKRel_{\Sign}}$ ensures that \ExtractSign must output a valid
  witness for $(\msg,\feval,\yeval^0,\ceval,\cinsp,\sipk_{\scred},\Eek,
  \widetilde{\Eek})$. Note that this witness must include some \usk which,
  for \adv~to win the game, must belong to an honest user. However, since the
  user (whichever it is) has not been corrupted, its \usk has not been leaked
  to \adv~via corruption queries (nor via \SIGN queries, where the proof of
  knowledge within \Sign is now simulated). Moreover, blindness of \SBCM ensures
  that the issuer (who is potentially corrupt), did not learn \usk either during
  calls to \OBTAIN. Thus, the probability that $\UK[\uid] = \usk$ for $\uid \in
  \HU$ and \Sig produced by the adversary, is negligible.
  %
  \qed
\end{proof}

>>>>

  If the verification at line 4 of \ExpForgeSign holds, then $(\msg,\feval,
  \yeval,\cinsp,\sipk,\opk) \in \NIZKLang^{\Sign}$. Then:
  %

  \paragraph{(a) \Judge accepts $(\yinsp,\iproof)$.} %
  Simulation extractability of $\NIZK^{\Sign}$ thus ensures that $\cinsp =
  \EEnc(\Eek,\yinsp)$, and since $(\yinsp,\iproof)$ is generated honestly at
  line 5, then \yinsp is the correct decryption of \cinsp, and completeness of
  $\NIZK^{\Open}$ ensures that \Judge outputs $1$ at line 6.

@@

  \paragraph{(c) The output of \finsp matches the output of \Open.} %
  After (a), and correctness of the public key encryption algorihtm, the \yinsp
  value output by \Open is the correct decryption of
  \cinsp. After (b), the $(\yeval^0=\yeval,\yeval^1)$ values output by
  \ExtractSign match the evaluation of \feval. Thus, simulation extractability
  of $\NIZK^{\Sign}$ ensures that $\finsp((\yeval^0,\yeval^1),\upk,\lbrace
  (\cid_i,\attrs_i)\rbrace_{i\in[n]},\msg) = \yinsp$ and, also, that \yinsp
  matches the $\yinsp'$ value extracted by \ExtractSign. Thus, the probability
  of \adv~winning at line 10 is negligible due to simulation extractability
  of $\NIZK^{\Sign}$.

  \paragraph{(d) All {\cred}s are bound to the same \usk.} %
  $\NIZKRel^{\Sign}$ includes a condition that $\forall i\in[n],
  \SBCMVerify(\ipk_i,\cred_i,\usk,\attrs_i) = 1$. Thus, simulation
  extractability of $\NIZK^{\Sign}$ and correctness of \SBCM, ensure that all
  credentials involved in the signature contain the same \usk as their user key
  (first) attribute. Thus, either $\OWNR[\lbrace \cid_i \rbrace_{i\in[n]}]$
  returns some \uid in $\HU \cup \CU$, or it returns $\bot$ because no such
  \uid exists (but not because more than one \cid belongs to different {\uid}s).
  Assume that no such \uid exists. Clearly, such a signature breaks the one-more
  forgery property of \SBCM, as it cannot have been produced via a call to
  \SIGN, which only accepts {\cid}s that belong to known {\uid}s. Therefore, the
  probability that \adv~wins at line 11 is negligible, given simulation
  extractability of $\NIZK^{\Sign}$, and correctness and one-more forgery
  security of \SBCM.
  %
  \qed
\end{proof}

@@

  First, suppose that, in the check done at line 10, the \Sig that \adv~outputs
  at line 2 exists in \SIG, for some \uid. In that case, given that the
  signature is accepted by \Verify at
  line 3, and after simulation extractability of $\NIZK^{\Sign}$, $\yeval =
  \yeval^0$, and $\tyeval^1 = \yeval^1$. Similarly, since the $(\yinsp,\iproof)$
  pair output by \adv~is accepted by \Judge, simulation extractability of
  $\NIZK^{\Sign}$ and $\NIZK^{\Open}$ implies that both checks at lines 7 and 8
  pass. Hence, the probability that the adversary wins at either lines 7 or 8 is
  negligible, after simulation extractability of $\NIZK^{\Sign}$ and
  $\NIZK^{\Open}$.

@@

  Consider game $G_1$, which is equivalent to $G_0 = \ExpNonframe$, except that
  in the \Sign function within the \SIGN oracle, we simulate the NIZK proof.
  After the zero-knowledge property of $\NIZK^{\NIZKRel_{\Sign}}$, $G_1$ is
  indistinguishable from $G_0$. Now, in $G_1$, simulation extractability of
  $\NIZK^{\NIZKRel_{\Sign}}$ ensures that \ExtractSign must output a valid
  witness for $(\msg,\feval,\yeval^0,\cinsp,\lbrace ipk_i \rbrace_{i\in[n]},
  \Eek)$. Note that this witness must include some \usk which,
  for \adv~to win the game, must belong to an honest user. However, since the
  user (whichever it is) has not been corrupted, its \usk has not been leaked
  to \adv~via corruption queries (nor via \SIGN queries, where the proof of
  knowledge within \Sign is now simulated). Moreover, blindness of \SBCM ensures
  that the issuer (who is potentially corrupt), did not learn \usk either during
  calls to \OBTAIN. Thus, the probability that $\UK[\uid] = \usk$ for $\uid \in
  \HU$ and \Sig produced by the adversary, is negligible.
  %
  \qed
\end{proof}

### 2022-08-08 prism-backend/research/gsac/formal-uas.tex
Updated proofs for sign-unforgeability, and non-frameability.

\begin{description}
\item[$\mathsf{H}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
  track of honest users/issuers/openers. They are sets of
  {\uid}s/{\iid}s/{\oid}s.
\item[$\mathsf{C}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
  track of corrupt users/issuers/openers. They are sets of
  {\uid}s/{\iid}s/{\oid}s.    
\item[\UK, \PUBUK and \PRVUK.] \UK maintains user key pairs $(\upk,\usk)$. To
  refer to the key of a specific user, we use $\UK[\uid]$. \PUBUK indexes the
  public keys, and \PRVUK the private keys.
\item[\IK, \PUBIK and \PRVIK.] \IK maintains issuer key pairs, where
  $\IK[\iid]$ refers to the key pair of the issuer with identifier \iid. We
  use \PUBIK to refer to the public component, which also includes the \fissue
  function; and \PRVIK refers to the private component of the key pair.
\item[\OK, \PUBOK, \PRVOK.] Same as \IK, but for opener key pairs. Instead
  of \fissue, \OK includes the \finsp function.
\item[\CRED.] Stores information related to credentials obtained by users in
  the system. Thus, it is indexable by \cid. More specifically, it stores
  tuples of the form $(\uid,\cred,\iid,\attrs,n,\lbrace (\cid_i,\iid_i)
  \rbrace_{i \in [n]})$, where \uid is the identifier of the owner of the
  credential, \cred (when available) is the credential itself, \iid is the
  identifier of the credential issuer, \attrs are the attributes included in
  \cred, $n$ is the number of credentials used to support this request, and
  $(\cid_i,\iid_i)$ for $i \in [n]$ are the corresponding credential and issuer
  identifiers. For notational convenience, we may use $\CRED[\scid]$
  to refer to $\CRED[\cid]$ for all {\cid}s in a set \scid. Also, when clear
  from context, we sometimes use $\CRED[\cid]$ (resp. $\CRED[\scid]$ to
  mean \cred (resp. \scred) in $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,
  \cdot,\cdot)$ (resp. $\CRED[\scid]$).
\item[\CCRED.] Like \CRED, but keeps track of challenge credentials in the
  issuance anonymity game.
\item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
  ``\uid such that $\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot)$''. We
  may also use \OWNR over a set of {\cid}s (\scid). In that case, our convention
  is that $\OWNR[\scid]$ returns $\bot$ if not all passed {\cid}s belong to the
  same \uid. Since $\bot$ is not a valid \uid, all conditions checking
  membership of the output of \OWNR to a list of users equal false if \OWNR
  returns $\bot$.
\item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
  ``\attrs such that $\CRED[\cid] = (\cdot,\cdot,\cdot,\attrs,\cdot,\cdot)$''.
\item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
  ``\iid such that $\CRED[\cid] = (\cdot,\cdot,\iid,\cdot,\cdot,\cdot)$''.
\item[\SIG.] Maintains signatures generated via the \SIGN oracle. Entries of
  this table are $(\oid,\scid,\sig,\Yeval,\msg,\feval)$ tuples, where \oid is
  the opener, \scid is the set of identifiers of the credentials used for
  signing, \feval is the signing evaluation function, and \sig and \msg are the
  produced signature and signed message.
\item[\CSIG.] Maintains challenge signatures output to the adversary in the
  signature anonymity game, and is indexable by challenge signatures \csig.
  Each entry contains also $\cuid_b$ and $\cscid_b$, respectively the challenge
  user  and credential identifiers set used to produce \csig; as well as the
  corresponding challenge user and credential set indexed by the complementary
  $1-b$; the signed message \msg and signing evaluation function \feval, the
  result of \feval, \Yeval, and the opener identifier \oid.
\end{description}

@@

\begin{theorem}[Signing unforgeability of \CUASGen]
  \label{thm:sign-forge-uas}
  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is simulation
  extractable,the NIZK scheme for $\NIZKRel_{\Open}$ is complete, the public-key
  encryption scheme is correct, and \SBCM is correct and one-more unforgeable,
  then our \CUASGen construction satisfies signing unforgeability as defined in
  \defref{def:sign-forge-uas}, except with negligible probability.
\end{theorem}

>>>>

\begin{description}
\item[$\mathsf{H}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
  track of honest users/issuers/openers. They are sets of
  {\uid}s/{\iid}s/{\oid}s.
\item[$\mathsf{C}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
  track of corrupt users/issuers/openers. They are sets of
  {\uid}s/{\iid}s/{\oid}s.    
\item[\UK, \PUBUK and \PRVUK.] \UK maintains user key pairs $(\upk,\usk)$. To
  refer to the key of a specific user, we use $\UK[\uid]$. \PUBUK indexes the
  public keys, and \PRVUK the private keys.
\item[\IK, \PUBIK and \PRVIK.] \IK maintains issuer key pairs, where
  $\IK[\iid]$ refers to the key pair of the issuer with identifier \iid. We
  use \PUBIK to refer to the public component, which also includes the \fissue
  function; and \PRVIK refers to the private component of the key pair.
\item[\OK, \PUBOK, \PRVOK.] Same as \IK, but for opener key pairs. Instead
  of \fissue, \OK includes the \finsp function.
\item[\CRED.] Stores information related to credentials obtained by users in
  the system. Thus, it is indexable by \cid. More specifically, it stores
  tuples of the form $(\uid,\cred,\iid,\attrs,n,\lbrace (\cid_i,\iid_i)
  \rbrace_{i \in [n]})$, where \uid is the identifier of the owner of the
  credential, \cred (when available) is the credential itself, \iid is the
  identifier of the credential issuer, \attrs are the attributes included in
  \cred, $n$ is the number of credentials used to support this request, and
  $(\cid_i,\iid_i)$ for $i \in [n]$ are the corresponding credential and issuer
  identifiers. For notational convenience, we may use $\CRED[\scid]$
  to refer to $\CRED[\cid]$ for all {\cid}s in a set \scid. Also, when clear
  from context, we sometimes use $\CRED[\cid]$ (resp. $\CRED[\scid]$ to
  mean \cred (resp. \scred) in $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,
  \cdot,\cdot)$ (resp. $\CRED[\scid]$).
\item[\CCRED.] Like \CRED, but keeps track of challenge credentials in the
  issuance anonymity game.
\item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
  ``\uid such that $\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot)$'', or
  $\bot$ if there is no wuch \uid. We may also use \OWNR over a set of {\cid}s
  (\scid). In that case, our convention is that $\OWNR[\scid]$ returns $\bot$ if
  not all passed {\cid}s belong to the same \uid. Since $\bot$ is not a valid
  \uid, all conditions checking membership of the output of \OWNR to a list of
  users equal false if \OWNR returns $\bot$.
\item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
  ``\attrs such that $\CRED[\cid] = (\cdot,\cdot,\cdot,\attrs,\cdot,\cdot)$''.
\item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
  ``\iid such that $\CRED[\cid] = (\cdot,\cdot,\iid,\cdot,\cdot,\cdot)$''.
\item[\SIG.] Maintains signatures generated via the \SIGN oracle. Entries of
  this table are $(\oid,\scid,\sig,\Yeval,\msg,\feval)$ tuples, where \oid is
  the opener, \scid is the set of identifiers of the credentials used for
  signing, \feval is the signing evaluation function, and \sig and \msg are the
  produced signature and signed message.
\item[\CSIG.] Maintains challenge signatures output to the adversary in the
  signature anonymity game, and is indexable by challenge signatures \csig.
  Each entry contains also $\cuid_b$ and $\cscid_b$, respectively the challenge
  user  and credential identifiers set used to produce \csig; as well as the
  corresponding challenge user and credential set indexed by the complementary
  $1-b$; the signed message \msg and signing evaluation function \feval, the
  result of \feval, \Yeval, and the opener identifier \oid.
\end{description}

@@

\begin{theorem}[Signing unforgeability of \CUASGen]
  \label{thm:sign-forge-uas}
  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is simulation
  extractable, the scheme for $\NIZKRel_{\Open}$ is complete, the public key
  encryption algorithm is correct, and the \SBCM scheme is correct and one-more
  unforgeable, then our \CUASGen construction satisfies signing unforgeability
  as defined in \defref{def:sign-forge-uas}, except with negligible probability.
\end{theorem}
